Title

### 2019-05-03 4_method.tex
MAT distance remapping and the cutoff point for markings

\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
\caption{Stability against extra vertices}
\label{finger_angles_stability}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
\end{subfigure}
\caption{Figner angles should always be orthogonal}
\label{finger_angles}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
\end{subfigure}
\caption{We can do single-bead segments. Blue is travel move.}
\label{single_bead_strategy}
\end{figure}

@@

The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices:t
\begin{figure}[H]
\centering
\includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
\end{figure}

\subsection{Where to round distance measures?}
\Cref{rounded_dist_measures}
Based on where the medial axis stops being of high curvature.

We mark bones as to-be-split based on the angle between the two edges of the polygon for which this bone is the bisector.
Parabolas are always to-be-split, since all points on the parabola are equidistant, so not rounding would introduce a gap along the parabola.
%For parabolas we check the angle between the three points involved: the end points of the line segment and the point which together generate the parabola. That angle is never less than \SI{90}{\degree}.

\hl{Is it impossible for three marked edges to come together?}

When a vertex in the medial axis has only a part of the connected bones marked then the distance measure should be rounded?
But that isn't stable against perturbations such as \cref{finger_angles_stability}!

>>>>

\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
\caption{Stability against extra vertices}
\label{finger_angles_stability}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
\end{subfigure}
\caption{Figner angles should always be orthogonal to the outlines}
\label{finger_angles}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
\caption{Overview}
\label{single_bead_strategy_overview}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
\caption{Travel order}
\end{subfigure}
\caption{We can do single-bead segments. Blue is travel move.}
\label{single_bead_strategy}
\end{figure}

@@

The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices:t
\begin{figure}[H]
\centering
\includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
\caption{Minimal Euclidean distance for a given difference in MAT distance measure.}
\label{distance_ratio_limit}
\end{figure}

\subsection{Determining which parts of the MAT should be transformed}
\Cref{rounded_dist_measures}
\paragraph{line-line-segments}
We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.

\paragraph{line-point segments}
For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
The angle between the outline segments is twice the angle between the MAT segment and an outline segment.
The angle between the MAT parabola and the x-axis is the inverse tangent of the derivative of this formula: $\tan^{-1} \left( \abs x / d \right)$.
The angle is less than \SI{60}{\degree} when 
$\tan^{-1} \left( \abs x / d \right) < \SI{30}{\degree}$ 
i.e. when $\abs x/d < 1 / \sqrt{3}$
i.e. when $\abs x < d / \sqrt{3}$.
So we mark the part of the parabola as to-be-transformed for which $x \in [-d / \sqrt{3}, d / \sqrt{3}]$.

\paragraph{point-point segments}
For a segment gerenated by points $(0,0)$ and $(0,d)$, the MAT segment is given by $y=\frac12 d$.
For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + \frac12 d}$.
The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{x}{\sqrt{x^2 + d/2}}$
So the Euclidean distance is more than twice the MAT distance then $\abs \frac{\partial D}{\partial x}  < \frac12$, 
%Wolfram Alpha:
so $\abs x < \frac{\sqrt{d}}{\sqrt{6}} \approx 0.408 d$.
So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.
\hl{But that is very weird in combination with the rule that the ends of marked segments should always be rounded! Isn't it?!}

\subsection{Ends of markings}
For vertices at the end of a sequence of marked MAT segments we need to perform rounding on the MAT distance measure, so as to avoid a gap being generated by toolapths around that vertex.
See bottom of \cref{rounded_vs_unrounded}.

It impossible for three marked edges to come together.
(Simple case) If 2 edges of the MAT meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.

However, \hl{what if we connect two marked segments using a small segment?}
It seems there is some distance limit based on \cref{distance_ratio_limit}.

\subsection{MAT distance remapping}
In a narrow cusp region we have to transfer from $n$ to $n-1$ beads; this transition requires a distance.
See \cref{single_bead_strategy_overview}.
We use a distance of the median bead width for the transition.
The transition needs to be robust against extra fingers in the MAT
How do we compute the vertex location of an inset on a finger which crosses a transitional segment in the middle?

By aligning the MAT distance with Euclidean space around the transition locations, we obtain a stable method for determining the vertex locations of insets.
See \cref{distance_rounding_transition}.
The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).

\begin{figure}[H]
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_rounding_transition.pdf}
\caption{MAT distance remapping.}
\label{distance_rounding_transition}
\end{figure}

\subsection{Where to round distance measures?}
When a vertex in the medial axis has only a part of the connected bones marked then the distance measure should be rounded?
But that isn't stable against perturbations such as \cref{finger_angles_stability}!
